---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
options(scipen=999) # to stop scientific notation

```

```{css}
.dynamic-comment {
background-color: darkblue;
}

```

## What's going on with this data?

I undertook a survey to find out how my TikTok feed changes throughout the day over the course of a week by viewing at least 15 videos on the app every day and at 4 periods throughout a day.

```{r}
#reading in logged data from survey

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/1ZMfGGBkD1fuwHL7aVNMg1PuUgaE6lp283xcpjwWJe-E/export?format=csv")

#renaming the logged_data table as tiktok_feed and relabelling the column headings
tiktok_feed <- logged_data %>%
  rename(timestamp = 'Timestamp',
         time_obs = 'What time is this observation being recorded?', 
         num_videos = 'How many videos did you watch? (At least 10 required)',
         content_type = 'What is the most common content type in your feed?', 
         av_vid_length = 'What was the average video length (in seconds)?', 
         engage_level = 'How engaging were the videos overall')

#checking table to see if ok
view(tiktok_feed)

#transforming engagement levels into factors
tiktok_feed <- tiktok_feed %>%     
  mutate(engage_level = factor(engage_level,
  levels = c("Not engaging", "Somewhat engaging", "Very engaging")))

```

`r nrow(tiktok_feed)` observations were recorded in this survey which logged my Tikok feed for most common content type, average video length and the overall level of engagement I felt from watching the videos.

```{r}
#Two summary values for Part D
#Average video length from those watched
overall_av_length = round(mean(tiktok_feed$av_vid_length, na.rm = TRUE), 1)

#Total number of videos watched across the week that observations were logged
total_videos = sum(tiktok_feed$num_videos)

```

The total number of videos watched was `r total_videos` videos and the average length of all videos watched was `r overall_av_length` seconds.

## Content type in my Tiktok feed 

```{r}

#First bar plot for Part D, most common content type in tiktok feed
tiktok_feed %>%
  ggplot(aes(x = content_type, fill = content_type)) +
  geom_bar() +
  scale_y_continuous(labels = function(x) ceiling(x)) +
  theme_minimal() +
  labs(title = "Most common content types in my Tiktok feed",
       x = "Tiktok content types",
       y = "Count ", 
       caption = "Source: STATS 220 survey S126")

#summing the totals for each category and sorting my highest to lowest
sum_cat <- tiktok_feed %>%
  count(content_type) %>%
  arrange(desc(n))

# Use this sum_cat[1,1] to get the category with the highest count

```

The graph shows that 'Lifestyle' content was the most frequently observed category in my TikTok feed. This suggests that the algorithm is strongly tailored toward content related to everyday living topics that I'm interested in such as DIY and frugal living. Other content types appeared less frequently, indicating that my feed is not evenly distributed across categories.

## Level of engagement with videos in Tiktok feed

```{r}
 
#Second bar plot for Part D, total level of engagement across all videos

tiktok_feed %>%
  ggplot(aes(x = engage_level, fill = engage_level)) +
  geom_bar() +
  #to round up y labels to whole numbers
  scale_y_continuous(labels = function(x) ceiling(x)) +
  theme_minimal() +
  labs(title = "Level of engagement in Tiktok feed",
       x = "Engagement level",
       y = "Count",
       caption = "Source: STATS 220 survey S126")

#summing the totals for each engagement level and sorting my highest to lowest
sum_eng_levels <- tiktok_feed %>%
  count(engage_level) %>%
  arrange(desc(n))

```

The bar chart indicates that the “somewhat engaging” videos were  frequently observed in my TikTok feed. Very few videos were classified as “not engaging”, suggesting that most of the content I watch on TikTok is mostly engaging. This reflects how TikTok’s algorithm tends to prioritise content that keeps users interested.

## Engagement by time of day

```{r}

#convert to factors with easy to understand labels
tiktok_feed <- tiktok_feed %>%
  mutate(time_obs = factor(time_obs,
      levels = c("06:00:00", "12:00:00", "18:00:00", "00:00:00"),
      labels = c("6am", "12pm", "6pm", "12am")
   )
)

#working out the level of engagement proportion recorded for each hour period
tiktok_feed %>%
  filter(!is.na(engage_level)) %>%
  count(time_obs, engage_level) %>%
  group_by(time_obs) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = time_obs, y = prop, fill = engage_level)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal() +
  labs(
    title = "Engagement level by time of day",
    x = "Time of observation",
    y = "Proportion",
    fill = "Engagement level")

```

This graph compares engagement levels across different times of the day. The proportions show that engagement was relatively consistent, with “somewhat engaging” content dominating at all times. This suggests that the overall quality of content in my TikTok feed does not vary significantly depending on when I access the app.

## Overall

Overall, the analysis shows that my TikTok feed is dominated by 'Lifestyle' content and generally consists of 'Somewhat engaging' to 'Very engaging' videos. While some variation exists across different times of the day, the overall patterns remain consistent, suggesting that TikTok’s algorithm delivers a stable and personalised content experience.