---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
options(scipen=999) # to stop scientific notation

```

```{css}
.dynamic-comment {
background-color: lightblue;
}

```
## What's going on with this data?
#logging how the my tiktok feed changes over the course of a week
#find out the main content thats coming through to my feed
#find out the average length of videos that I watch

```{r}
#reading in logged data from survey

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/1ZMfGGBkD1fuwHL7aVNMg1PuUgaE6lp283xcpjwWJe-E/export?format=csv")

#renaming the table and the column headings
tiktok_feed <- logged_data %>%
  rename(time_obs = 2, num_videos = 3,
         content_type = 4, av_vid_length = 5, 
         engage_level = 6)

#checking table to see if ok
view(tiktok_feed)

```
`r nrow(tiktok_feed)` observations were recorded in this survey which logged my tiktok feed for most common content type, average video length and the overall level of engagement I felt from watching the videos.

```{r}
#Two summary values for Part D
#Average video length from those watched
overall_av_length = round(mean(tiktok_feed$av_vid_length, na.rm = TRUE), 1)

#Total number of videos watched across the week that observations were logged
total_videos = sum(tiktok_feed$num_videos)

#paste0("The total number of videos watched was ", total_videos, " videos and the average length of all videos watched was ",      overall_av_length, " seconds.")


```

The total number of videos watched was `r total_videos` videos and the average length of all videos watched was `r overall_av_length` seconds.

## Content type in my Tiktok feed 

```{r fig.width = 8, fig.height = 8}
 
#First bar plot for Part D, most common content type in tiktok feed
tiktok_feed %>%
  ggplot(aes(x = content_type)) +
  geom_bar() +
  scale_y_continuous(labels = function(x) ceiling(x)) +
  theme_minimal() +
  labs(title = "Most common content types in my tiktok feed",
       x = "Content types in tiktok feed",
       y = "Count ", 
       caption = "Source: STATS 220 survey S126")

#summing the totals for each category and sorting my highest to lowest
sum_cat <- tiktok_feed %>%
  count(content_type) %>%
  arrange(desc(n))

# Use this sum_cat[1,1] to get the category with the highest count

```

The content type most frequently in my tiktok feed is '`r sum_cat[1,1]`'.


## Level of engagement with videos in tiktok feed

```{r fig.width = 8, fig.height = 8}
 
#Second bar plot for Part D, total level of engagement across all videos

tiktok_feed %>%
  ggplot(aes(x = engage_level)) +
  geom_bar() +
  scale_y_continuous(labels = function(x) ceiling(x)) +
  theme_minimal() +
  labs(title = "Level of engagement in tiktok feed",
       x = "Level of engagement from Tiktok feed",
       y = "Count",
       caption = "Source: STATS 220 survey S126")

sum_eng_levels <- tiktok_feed %>%
  count(engage_level) %>%
  arrange(desc(n))

```

The engagement levels in my tiktok feed were '`r sum_eng_levels[1,1]`'.


